---
title: Full title of the paper (Capitalized)
author:
  - name: Amrita Acharya
    affil: 1,2,\ddagger,*
  - name: Dianne Caravela
    affil: 2, \dagger, \ddagger
  - name: Eunice Kim
    affil: 3
  - name: Emma Kornberg
    affil: 4
  - name: Elisabeth Nesmith
    affil: 5
affiliation:
  - num: 1
    address: |
      Statistical and Data Sciences
      Smith College
      Northampton, MA 01063
    email: aacharya@smith.edu
  - num: 2
    address: |
      Smith College
    email: dcaravela@smith.edu
# firstnote to eighthnote
firstnote: |
  Current address: Updated affiliation
secondnote: |
  These authors contributed equally to this work.
correspondence: |
  leutnant@fh-muenster.de; Tel.: +XX-000-00-0000.
journal: water
type: article
status: submit
bibliography: mybibfile.bib
csl: ../resources/chicago-author-date.csl
appendix: appendix.tex
simplesummary: |
  A Simple summary goes here.
abstract: |
  A single paragraph of about 200 words maximum. For research articles, 
  abstracts should give a pertinent overview of the work. We strongly encourage
  authors to use the following style of structured abstracts, but without 
  headings: 1) Background: Place the question addressed in a broad context and
  highlight the purpose of the study; 2) Methods: Describe briefly the main
  methods or treatments applied; 3) Results: Summarize the article's main 
  findings; and 4) Conclusion: Indicate the main conclusions or interpretations. 
  The abstract should be an objective representation of the article, it must not 
  contain results which are not presented and substantiated in the main text and 
  should not exaggerate the main conclusions.
keywords: |
  keyword 1; keyword 2; keyword 3 (list three to ten pertinent keywords specific 
  to the article, yet reasonably common within the subject discipline.).
acknowledgement: |
  All sources of funding of the study should be disclosed. Please clearly 
  indicate grants that you have received in support of your research work. 
  Clearly state if you received funds for covering the costs to publish in open 
  access.
authorcontributions: |
  For research articles with several authors, a short paragraph specifying their 
  individual contributions must be provided. The following statements should be 
  used ``X.X. and Y.Y. conceive and designed the experiments; X.X. performed the 
  experiments; X.X. and Y.Y. analyzed the data; W.W. contributed 
  reagents/materials/analysis tools; Y.Y. wrote the paper.'' Authorship must be
  limited to those who have contributed substantially to the work reported.
conflictsofinterest: |
  Declare conflicts of interest or state 'The authors declare no conflict of 
  interest.' Authors must identify and declare any personal circumstances or
  interest that may be perceived as inappropriately influencing the
  representation or interpretation of reported research results. Any role of the
  funding sponsors in the design of the study; in the collection, analyses or 
  interpretation of data in the writing of the manuscript, or in the decision to 
  publish the results must be declared in this section. If there is no role, 
  please state 'The founding sponsors had no role in the design of the study; 
  in the collection, analyses, or interpretation of data; in the writing of the 
  manuscript, an in the decision to publish the results'.
sampleavailability: |
  Samples of the compounds ...... are available from the authors.
abbreviations:
  - short: MDPI
    long: Multidisciplinary Digital Publishing Institute
  - short: DOAJ
    long: Directory of open access journals
  - short: TLA
    long: Three letter acronym
  - short: LD 
    long: linear dichroism
output: rticles::mdpi_article
---

# Version

This Rmd-skeleton uses the mdpi Latex template published 2019/02. 
However, the official template gets more frequently updated than the 'rticles'
package. Therefore, please make sure prior to paper submission, that you're 
using the most recent .cls, .tex and .bst files 
(available [here](http://www.mdpi.com/authors/latex)).

# Introduction

A recidivist is a term to describe criminals who re-offend. 

# Data

The data we are using for this project is the Correctional Offender Management Profiling for Alternative Sanctions (COMPAS) Recidivism Risk Scores dataset from AIF360. Northpointe created COMPAS as a commercial risk assessment tool to score defendants on their potential recidivism and violent recidivism risk. The COMPAS dataset we are using has 6,167 rows and each row represents an arrest charge for a defendant. We also have data on the defendant's age, race, sex, what they were charged with, and whether or not the defendant ultimately recidivated. 

# Results

This section may be divided by subheadings. It should provide a concise and precise description of the experimental results, their interpretation as well as the experimental conclusions that can be drawn.

## Subsection Heading Here

Subsection text here.

### Subsubsection Heading Here

Bulleted lists look like this:

* First bullet
* Second bullet
* Third bullet

Numbered lists can be added as follows:

1. First item
2. Second item
3. Third item

See Figure \ref{fig:random-plot} below.

```{r random-plot, fig.cap="This is a plot.", fig.align='center'}
plot(rnorm(10), rnorm(10))
```



The text continues here.

All figures and tables should be cited in the main text as Figure \ref{fig:mdpi-logo}, Table 1, etc.

```{r mdpi-logo, fig.align='center', echo=FALSE, fig.cap="This is a figure, Schemes follow the same formatting. If there are multiple panels, they should be listed as: (\\textbf{a}) Description of what is contained in the first panel. (\\textbf{b}) Description of what is contained in the second panel. Figures should be placed in the main text near to the first time they are cited. A caption on a single line should be centered."}

# Ben's tutorial on how to include figures with R code chunk
knitr::include_graphics("logo-mdpi.pdf")
```


Please see Table \ref{tab:mytable}.

```{r}
x <- tibble::tribble(~`Title 1`, ~`Title 2`, ~`Title 3`,
"entry 1", "data", "data",
"entry 2", "data", "data"
)

knitr::kable(x, caption = "This is a table caption. Tables should be placed in the main text near to the first time they are cited.\\label{tab:mytable}")
```


This is an example of an equation:

\begin{equation}
\mathbb{S}
\end{equation}
<!-- If the documentclass option "submit" is chosen, please insert a blank line before and after any math environment (equation and eqnarray environments). This ensures correct linenumbering. The blank line should be removed when the documentclass option is changed to "accept" because the text following an equation should not be a new paragraph. -->

<!-- Please punctuate equations as regular text. Theorem-type environments (including propositions, lemmas, corollaries etc.) can be formatted as follows: -->
Example of a theorem:
\begin{Theorem}
Example text of a theorem.
\end{Theorem}

The text continues here. Proofs must be formatted as follows:

Example of a proof:
\begin{proof}[Proof of Theorem 1]
Text of the proof. Note that the phrase `of Theorem 1' is optional if it is clear which theorem is being referred to.
\end{proof}
The text continues here.

# Discussion

Authors should discuss the results and how they can be interpreted in perspective of previous studies and of the working hypotheses. The findings and their implications should be discussed in the broadest context possible. Future research directions may also be highlighted.

# Conclusion

This section is not mandatory, but can be added to the manuscript if the discussion is unusually long or complex.

# Bibliography

@angwin2016machine
@bao2021s
@barocas2017fairness
@baumer2017texts
@equivant_response_2018
@gebru2021datasheets
@hardin2015data
@james2013introduction
@knight2020automated
@kypraiou_what_2021
@larson2016technical
@larson2016we
@noauthor_ai_nodate
@noauthor_aif360datasetscompasdataset_2018
@noauthor_trusted-ai_360
@noauthor_propublicacompas-analysis_2022
@noauthor_womenthetable_nodate
@vartan_1st_2022
